\documentclass[conference,10pt]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\graphicspath{./graphics/}
\usepackage{tabularx}
\usepackage{cite}
\usepackage{url}
\usepackage{enumerate}
\usepackage[dvipsnames]{xcolor}
\usepackage{wasysym}
\usepackage{gensymb}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{dateplot}
\usepackage{macros}
\def\NewL{\\\noindent\hspace*{5mm}}
\begin{document}
\title{Detection of Constant Phase Shifts in\\Filters for Sound Field Synthesis\\
{\footnotesize Submission as abstract reviewed paper for 5th International
Conference on Spatial Audio (ICSA), Ilmenau, Germany, September 2019}}
\author{\IEEEauthorblockN{Frank Schultz, Nara Hahn, Sascha Spors}
\IEEEauthorblockA{\textit{Institute of Communications Engineering,
University of Rostock}\\
Rostock, Germany\\
\{frank.schultz, nara.hahn, sascha.spors\}@uni-rostock.de}
}
\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\begin{abstract}
\input{sections/abstract.tex}
\end{abstract}
\begin{IEEEkeywords}
constant phase shift, fractional Hilbert transform, audibility of phase distortion
\end{IEEEkeywords}
\input{sections/introduction.tex}
\input{sections/constant-phase-shift.tex}
\input{sections/listening-experiment.tex}
\input{sections/conclusion.tex}
\input{sections/open-science.tex}
\renewcommand\refname{}
\section{References}
\bibliographystyle{IEEEtran}
\bibliography{bibliography}

\section*{Submitted Abstract}
The submitted abstract slightly varies from the final abstract, since not all
referred results found their way into the final version of the paper.
Therefore, we provide the submitted abstract as follows:
%
\NewL Filters with constant phase shift, often in conjunction with +-3/6 dB
amplitude decay per octave, frequently occur in sound field synthesis and
sound reinforcement applications.
%
These ideal filters are known as (half) differentiators/integrators and exhibit
zero group delay and +-45/90 degree phase shift.
%
It is well known that certain group delay distortions in electro-acoustic
systems are audible for trained listeners for critical audio stimuli, such as
transient, impulse-like and square wave signals.
%
It is of interest if linear distortion by a constant phase shift is audible
as well.
%
For that, we conducted a series of ABX listening tests, diotically presenting
non-phase shifted references against their treatments with different phase
shifts.
%
The experiments revealed that (similar to group delay) for the critical
square waves, this can be clearly detected, which generally depends on the
amount of constant phase.
%
Here, -90 degree (Hilbert transform) is comparably easier to detect than other
phase shifts. For castanets and pink-noise shaped Dirac impulse, the detection
rate tends to guessing for most listeners, although the polarity inversion
(+-180) is detectable, thereby confirming earlier studies on this topic.
%
Our results motivate to apply constant phase shift filters to ensure that also
the most critical signals are technically reproduced  as best as possible
(cf. modern electronic dance music with typical crest factor of as low as 6 dB).
%
In the paper, we furthermore give the analytical expressions for continuous
and discrete-time infinite impulse responses for unit magnitude filter with
arbitrary constant phase shift.

Submitted: Jun 23, 21:37 GMT

Last update:Jun 24, 07:06 GMT
\end{document}
